My wonderful paper

### 2024-10-24 _manuscript/_tex/index.tex
some dot points

>>>>

\begin{itemize}
\item
  multiple tests can be generated to diagnose different aspects of an
  analysis
\item
  good tests

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi})}
  \tightlist
  \item
    are responsive to an unexpected result - accuracy,
  \item
    motivate actions of analysts to investigate the results. This points
    towards a smaller set of independent tests
  \end{enumerate}
\item
  Since both the plan/ outcome expectations can be phrased as unit
  tests, which output binary outcomes, consider using the plan
  expectations as predictors of the outcome expectations. This allows to
  generate the confusion matrix of predicting the outcome with the plan
  expectation.
\item
  For an analysis, ideally, good plan expectations should maximize the
  detection of unexpected outcomes while minimize the false positive
  discovery, which suggest the use of precision and recall (REF) for
  evaluating the performance of the plan expectations.

  \begin{itemize}
  \tightlist
  \item
    precision: the proportion of unexpected results (TP) out of all the
    predicted unexpected results (TP + FP)
  \item
    recall: the proportion of unexpected results (TP) out of all the
    actual unexpected results (TP + FN)
  \end{itemize}
\item
  A logic regression (ref) is used to model the relationship between the
  plan and outcome expectations. (justify the use of Logic regression)
\item
  on independence of the tests
\end{itemize}

### 2024-10-24 index.qmd
some dot points

>>>>

- multiple tests can be generated to diagnose different aspects of an analysis 
- good tests 
    1) are responsive to an unexpected result - accuracy, 
    2) motivate actions of analysts to investigate the results. This points towards a smaller set of independent tests

- Since both the plan/ outcome expectations can be phrased as unit tests, which output binary outcomes, consider using the plan expectations as predictors of the outcome expectations. This allows to generate the confusion matrix of predicting the outcome with the plan expectation.

- For an analysis, ideally, good plan expectations should maximize the detection of unexpected outcomes while minimize the false positive discovery, which suggest the use of precision and recall (REF) for evaluating the performance of the plan expectations.

  * precision: the proportion of unexpected results (TP) out of all the predicted unexpected results (TP + FP)
  * recall: the proportion of unexpected results (TP) out of all the actual unexpected results (TP + FN)

* A logic regression (ref) is used to model the relationship between the plan and outcome expectations. (justify the use of Logic regression)

* on independence of the tests
